The letter

### 2010-06-29 ltx/PLoS/LaTeX_Manuscript.tex
Corrected some typos and added some comments to discuss

% TO DELETE
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
 % \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
 \documentclass[10pt]{article}

@@

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step. 
% Author Summary not valid for PLoS ONE submissions.   
\section*{Author Summary}
With recent advances in medical imaging techniques and computing power, we are entering a new age of neuroscientific research, where patient-specific information and experimental data is becoming incredibly detailed. In order to make the best use of this information, mathematical models should be formed. This is particularly poignant where considering poorly understood complex systems such as large-scale dynamics of the human brain. There currently exists a library of mathematical models describing large-scale brain dynamics, providing a theoretical explanation of various phenomena associated with various cognitive states and disease. In this paper, we have created a framework for creating a data-driven mathematical model, forming a bridge between theory and electrophysiological data. Within this framework, we propose rules for designing experiments and we derive the mathematical formula to create the model. To demonstrate the utility of this framework, we provide an example using synthetic data that shows a comparison between true and estimated model characteristics. The ability to create patient-specific models of large-scale brain dynamics has the potential to revolutionise the treatment of diseases such as epilepsy, where techniques from engineering may be used to prevent abnormal neural oscillations.

\section*{Introduction}
Generating physiologically plausible neural field models are of great importance for studying brain dynamics at the mesoscopic and macroscopic scale. While our understanding of the function of neurons is well developed, the overall behaviour of the brain's mesoscopic and macroscopic scale dynamics remains largely theoretical. Understanding the brain at this level is extremely important since it is at this scale that pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.

@@

where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface. The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and surround inhibition. An example of the connectivity kernel is shown in in Figure~\ref{fig:2d_kernel}. To demonstrate flexibility in the estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation. The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.

@@

where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}. This term is added to account for uncertainty and unmodelled inputs. To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.

@@

An analytic derivation of the inner product of \emph{n}-dimensional Gaussians is provided in the Supporting Information, S1. Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where

@@

which is a constant $L \times n_{\theta}$ matrix that can is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions. Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives

@@

This simplification has transformed the description of the spatial coupling from a convolution of the firing rates with the connectivity kernel, to a convolution of the of the connectivity kernel basis functions with the field basis functions. This transformation provides a dramatic increase in estimation speed, since the matrix $\Psi(\mathbf{r}')$ is constant an can be pre-defined analytically. This is of great importance considering the computational demands of the estimation algorithm.

@@

\subsection{Spectral Analysis and Model Selection}\label{SpectralAnalysisSection} Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}. Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.

@@

Alternatively, given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis. This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors. To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
\begin{equation}\label{eq:CutoffFromBasisFuncWidth}
	\boldsymbol{\nu}_{c\phi}=\frac{1}{\pi\sigma_{\phi}}\sqrt{\frac{\ln2}{2}}.
\end{equation}

@@

The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation. The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$. The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation. The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
\begin{align}\label{eq:sigmapoints1}
	\mathcal X_{0}&=\bar x \\
	\mathcal X_{i}&=\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L \\
	\mathcal X_{i}&=\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2L 
\end{align}
where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for the filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space. The total number of sigma points is $2L+1$. The scaling parameter, $\lambda$, is defined as 
\begin{equation}\label{eq:sigmapoints3}
	\lambda=\alpha^2( L+\kappa) - L, 
\end{equation}
where the constant $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).

@@

The sensors were spaced on a regular square $14 \times 14$ grid and the sensor width was set to $\sigma^2_m = 0.81$. This provides a width of 1.5~mm at half the maximum amplitude of the sensor kernel. The distance between sensors was set to $\Delta_y = 1.5$~mm. This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
 \begin{figure}
    	\begin{center}
     		\includegraphics{./Graph/ExperimentalFigure.pdf}
    	\end{center}
    	\caption{{\bf Example of the spatio-temporal properties of the model and synthetically generated data.} \textbf{(A)} The neural field at a single time instant. (\textbf{B}) Data generated by the full neural field model from the first 5 sensors. (\textbf{C}) Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.} 
 \label{fig:experimental design}
 \end{figure}
\subsection*{Spatial Frequency Analysis} 
Using the model selection techniques described in Section~\ref{SpectralAnalysisSection}, the spatial frequency analysis was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field. The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point). From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm. This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to prevent problems associated with spatial aliasing.
\begin{figure}
\centering
\label{fig:FieldFFT}\includegraphics{./Graph/FFTField.pdf}
\caption{{\bf Spatial frequency analysis of the neural field}. (\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field. (\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition. The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
\label{fig:FFTTrueEstimate}
\end{figure}

The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(A). The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz (-3~dB point). The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(B). Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}). The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to our criteria.
Given the basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm. This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}. The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(C). The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B). This figure illustrates the band-limiting effect of the basis function decomposition when compared to Figure~\ref{fig:FFTTrueEstimate}(A).
\begin{figure*}[!ht] 
	\begin{center}
		\includegraphics{./Graph/SensorBasisObsFrequencyResponse.pdf}	
	\end{center}
	\caption{{\bf Spatial frequency analysis}. The dashed line shows the cut-off frequency (-3 dB point). (\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations. (\textbf{B}) The spatial frequency response of a one-dimensional model sensor. The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics. (\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors.} 
	\label{fig:ObservationFreqAnal}
\end{figure*}
\subsection*{State and Parameter Estimates} 
\label{sec:state_and_param_results}
To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 100 realisations of the data were generated. Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out. The initial state and parameters were unknown to the estimator. Eleven iterations of the estimation algorithm were used to ensure the parameters  converged. Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameters falling to less than $10^{-4}$ after six iterations.
\begin{figure}
        \centering
\includegraphics{./Graph/convergence.pdf}
\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 100 runs. All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
\label{fig:ParametersConvergence}
\end{figure}

@@

The development of an estimation framework also has theoretical implications, where the ability to estimate parameters will allow testing of hypotheses that have been generated in computational modelling studies. This has the potential to validate neural field models, and in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics. For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions can exist. In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as sleep and anaesthesia.

>>>>

% TO DELETE
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}

 % \documentclass[twocolumn,10pt]{article}						%<-use this for checking equation length
 \documentclass[10pt]{article}

@@

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLoS ONE authors please skip this step. 
% Author Summary not valid for PLoS ONE submissions.   
\section*{Author Summary}
With recent advances in medical imaging techniques and computing power, we are entering a new age of neuroscientific research, where patient-specific information and experimental data is becoming incredibly detailed. In order to make the best use of this information, mathematical models should be formed. This is particularly poignant where considering poorly understood complex systems such as the large-scale dynamics of the human brain. There currently exists a library of mathematical models describing large-scale brain dynamics, providing a theoretical explanation of various phenomena associated with various cognitive states and diseases. In this paper, we have created a framework for creating a data-driven mathematical model, forming a bridge between theory and electrophysiological data. Within this framework, we propose rules for designing experiments and we derive the mathematical formula to create the model. To demonstrate the utility of this framework, we provide an example using synthetic data that shows a comparison between true and estimated model characteristics. The ability to create patient-specific models of large-scale brain dynamics has the potential to revolutionise the treatment of diseases such as epilepsy, where techniques from engineering may be used to prevent abnormal neural oscillations.

\section*{Introduction}
Generating physiologically plausible neural field models is of great importance for studying brain dynamics at the mesoscopic and macroscopic scale. While our understanding of the function of neurons is well developed, the overall behaviour of the brain's mesoscopic and macroscopic scale dynamics remains largely theoretical. Understanding the brain at this level is extremely important since it is at this scale that pathologies such as epilepsy, Parkinson's disease and schizophrenia are manifested.

@@

where $f(\cdot)$ is the firing rate function, $w(\cdot)$ is the spatial connectivity kernel and $\Omega$ is the spatial domain representing a cortical sheet or surface. The connectivity kernel is typically a ``Mexican hat'' function, which describes local excitation and surround inhibition. An example of the connectivity kernel is shown in Figure~\ref{fig:2d_kernel}. To demonstrate flexibility in the estimation algorithm, a third component of the kernel is introduced describing weak longer-range excitation. The exact shape of this kernel is assumed to vary across patients, and hence needs to be inferred from data.

@@

where $T_s$ is the time step, $\xi = 1-\zeta T_s$ and $e_t(\mathbf{r})$ is an $i.i.d.$ disturbance such that $e_t(\mathbf{r})\sim\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$. Here $\mathcal{GP}(\mathbf 0,\gamma(\mathbf{r}-\mathbf{r}'))$ denotes a zero mean spatial Gaussian process with covariance function $\gamma(\mathbf{r}-\mathbf{r}')$~\cite{Rasmussen2005}. This term is added to account for model uncertainty and unmodelled inputs. To simplify the notation, the index of the future time sample, $t+T_s$, shall be referred to as $t+1$ throughout the rest of the paper.

@@

An analytic derivation of the inner product of Equation~\ref{eq:DefGamma} of \emph{n}-dimensional Gaussians is provided in the Supporting Information, S1. Equation~\ref{eq:ReducedForm} can be simplified by exploiting the isotropy of the kernel and, hence, the basis functions used to represent it where

@@

which is a constant $L \times n_{\theta}$ matrix that can is defined analytically (see the Supporting Information, S1, for analytic convolution of two Gaussians as given by Equation~\ref{eq:DefPsi}), where $L$ is the number of basis functions (and states) and $n_{\theta}$ is the number of connectivity basis functions. Now substituting equation~\ref{eq:DefPsi} into~\ref{eq:ReducedForm} gives

@@

This simplification has transformed the description of the spatial coupling from a convolution of the firing rates with the connectivity kernel, to a convolution of the connectivity kernel basis functions with the field basis functions. This transformation provides a dramatic increase in estimation speed, since the matrix $\Psi(\mathbf{r}')$ is constant and can be pre-defined analytically. This is of great importance considering the computational demands of the estimation algorithm.

@@

\subsection{Spectral Analysis}\label{SpectralAnalysisSection} 
\ken{Guys, changed the name for this section cause it only contains spectral analysis and no real model selection. I can understand the argument that the spectral analysis leads to a model choice, but no model selection follows it. Thus I'd rather use this revised name.}
Spectral analysis has been used to identify both the number of sensors and the number of basis functions required to reconstruct the neural field from sampled observations~\cite{Sanner1992,Scerri2009}. Based on a two-dimensional extension of Shannon's sampling theorem \cite{Peterson1962}, the spatial bandwidth of the observed field can be used to provide a lower bound on both the number of sensors and the number of basis functions required to capture the dominant spectral characteristics of the neural field.

@@

\ken{I cannot understand the motivation being including this paragraph? I do not feel that this argument has any practical implications; can anyone enlighten me?}
Alternatively, given the basis function width, the spatial cut-off frequency of the field modelled by the decomposition can be determined from spectral analysis. This is particularly useful when considering the spatially distributed basis functions, since Shannon's sampling theorem is derived for perfect point sensors. To calculate the cut-off frequency imposed by the basis functions, $\boldsymbol{\nu}_{c\phi}$, we rearrange equations~\ref{eq:WidthCutOffRelationship} and \ref{eq:WidthFrequencyRelationship} giving
\begin{equation}\label{eq:CutoffFromBasisFuncWidth}
	\boldsymbol{\nu}_{c\phi}=\frac{1}{\pi\sigma_{\phi}}\sqrt{\frac{\ln2}{2}}.
\end{equation}

@@

The unscented Rauch-Tung-Striebel smoother (URTSS)~\cite{Sarkka2010} is used for the state estimation. The URTSS incorporates an unscented Kalman filter (UKF)~\cite{Julier1997, Merwe2003} in a forward step to estimate posterior states, $\hat{\mathbf x}_t^{f}$, followed by a backward step to compute the smoothed state estimates, $\hat{\mathbf x}_t^{b}$. The first and second order moments of the predicted state are captured by propagating the so-called sigma points through the state equation. The sigma points, $\mathcal X_i$, are calculated using the unscented transform as follows:
\begin{align}\label{eq:sigmapoints1}
	\mathcal X_{0}&=\bar x \\
	\mathcal X_{i}&=\bar x+\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i, \quad i=1, \dots, L \\
	\mathcal X_{i}&=\bar x-\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_{i- L}, \quad i= L+1, \dots, 2L 
\end{align}
where $\bar x$ represents either $\hat{\mathbf x}_t^{f}$ or $\hat{\mathbf x}_t^{b}$, $\mathbf{P}_x$ is the corresponding covariance matrix for filtering or smoothing, $\left(\sqrt{( L + \lambda)\mathbf P_x}\right)_i$ is the $i^{th}$ column of the scaled matrix square root of $\mathbf P_x$ and $L$ is the dimension of the state space. The total number of sigma points is $2L+1$. The scaling parameter, $\lambda$, is defined as 
\begin{equation}\label{eq:sigmapoints3}
	\lambda=\alpha^2( L+\kappa) - L, 
\end{equation}
where the constant $\alpha$ determines the spread of the sigma points, $\beta$ incorporates prior knowledge of the distribution of $\mathbf{x}$ and $\kappa$ is an additional scaling parameter (see~\cite{Haykin2001} for more details).

@@

The sensors were spaced on a regular square $14 \times 14$ grid and the sensor width was set to $\sigma^2_m = 0.81$. This provides a width of 1.5~mm at half the maximum amplitude of the sensor kernel. The distance between sensors was set to $\Delta_y = 1.5$~mm. This arrangement modelled the recording as having some cross talk, which is typical for neurophysiological recordings.
 \begin{figure}
    	\begin{center}
     		\includegraphics{./Graph/ExperimentalFigure.pdf}
    	\end{center}
    	\caption{{\bf Example of the spatio-temporal properties of the model and synthetically generated data.} \textbf{(A)} The neural field at a single time instant. (\textbf{B}) Data generated by the full neural field model from the first 5 sensors. (\textbf{C}) Power spectral density of the data generated by an observation showing the typical $1/f^2$ characteristic of intracranial EEG.} 
 \label{fig:experimental design}
 \end{figure}
\subsection*{Spatial Frequency Analysis} 
The spectral analysis described in Section~\ref{SpectralAnalysisSection} was used to confirm that the spacing and width of the sensors was adequate to capture the significant dynamics of the field. Figure~\ref{fig:FFTTrueEstimate}(A) shows the spatial frequency of the neural field. The cut-off frequency of the neural field is $\boldsymbol{\nu}_c \approx 0.24$~Hz ($-3$~dB point). From equation~\ref{eq:MinimumSensorDistance}, this yielded a minimum sensor separation of 2.05~mm. This confirms that the separation of $\Delta_{y} = 1.5$~mm was sufficient to mitigate problems associated with spatial aliasing.
\begin{figure}
\centering
\label{fig:FieldFFT}\includegraphics{./Graph/FFTField.pdf}
\caption{{\bf Spatial frequency analysis of the neural field}. (\textbf{A}) The average (over time) power in dB of the spatial frequency of the neural field. (\textbf{B}) The average (over time) power in dB of the spatial frequency of the reconstructed neural field from the basis function decomposition. The reconstructed field shows a narrower bandwidth as a result of the band limiting properties of the sensors and basis functions.}
\label{fig:FFTTrueEstimate}
\end{figure}

The spatial frequency of the observed field is shown in Figure~\ref{fig:ObservationFreqAnal}(A). The cut-off frequency is $\boldsymbol{\nu}_{cy} \approx 0.2$~Hz (-3~dB point). The observation cut-off frequency is lower than the field cut-off due to the low-pass filtering effect of the sensors. The spatial frequency response of the sensors can be seen in Figure~\ref{fig:ObservationFreqAnal}(B). Using an oversampling parameter of $\rho_{\phi}=1$, the minimum distance between the field basis functions was calculated to be 2.5~mm to satisfy Shannon's sampling criterion (from equation~\ref{eq:BasisFunctionSeparation}). The distance between basis functions was set to $\Delta_{\phi}=2.5$~mm, which is sufficient to capture the significant dynamics according to these criteria.
Given this basis function separation, the basis function width parameter was set to $\sigma_{\phi}^2=2.5$~mm. This allowed a smooth representation of the field by the basis function decomposition up to a spatial frequency $\boldsymbol{\nu}_{c\phi} \approx 0.12$~Hz, as described by equation~\ref{eq:CutoffFromBasisFuncWidth}. The band-limiting effect is due to the spatial frequency response of the basis functions as seen in Figure~\ref{fig:ObservationFreqAnal}(C). The spatial frequency of the reconstructed field from the basis function decomposition is shown in Figure~\ref{fig:FFTTrueEstimate}(B). This figure illustrates the band-limiting effect of the basis function decomposition when compared to Figure~\ref{fig:FFTTrueEstimate}(A).
\begin{figure*}[!ht] 
	\begin{center}
		\includegraphics{./Graph/SensorBasisObsFrequencyResponse.pdf}	
	\end{center}
	\caption{{\bf Spatial frequency analysis}. The dashed line shows the cut-off frequency (-3 dB point). (\textbf{A}) The average (over time) power in dB of the spatial frequency of the observations. (\textbf{B}) The spatial frequency response of a one-dimensional model sensor. The symmetry of the sensors and field basis functions allow for the one-dimensional representation of the spectral characteristics. (\textbf{C}) The spatial frequency response of a one-dimensional neural field basis function, illustrating a narrower band width than the sensors. \ken{This is not correct!} } 
	\label{fig:ObservationFreqAnal}
\end{figure*}
\subsection*{State and Parameter Estimates} 
\label{sec:state_and_param_results}
To demonstrate the performance of the state and parameter estimation algorithm, a Monte Carlo approach was employed where 100 realisations of the data were generated. Each realisation consisted of 500~ms of data (sampled at $1$~kHz) and the estimation was applied to the final 400~ms, allowing the model's initial transients to die out. The initial state and parameters were unknown to the estimator. Eleven iterations of the estimation algorithm were used to ensure the parameters  converged. Figure~\ref{fig:ParametersConvergence} shows the rate of convergence, confirming the parameters converged, with the changes in parameters falling to less than $10^{-4}$ after six iterations.
\begin{figure}
        \centering
\includegraphics{./Graph/convergence.pdf}
\caption{{\bf Convergence of parameters.} The mean of the absolute error between true and estimated parameters averaged over 100 runs. All parameters converge after six iterations, where the mean difference between errors in consecutive iterations falls below $10^{-4}$.}
\label{fig:ParametersConvergence}
\end{figure}

@@

The development of an estimation framework also has theoretical implications, where the ability to estimate parameters will allow testing of hypotheses that have been generated in computational modelling studies. This has the potential to validate neural field models, and in doing so, provide new insights that may lead to a greater understanding of macro-scale neurodynamics. For example, using the proposed model-based framework, we can reconstruct a neural field from data and estimate parameters to check if they correspond to theoretically derived values where certain solutions may exist. In addition, the parameters and the state-space can be explored during cognitive tasks and states of arousal such as sleep and anaesthesia.
